---
title: "linearmodelwithprediction"
author: "Tyler Frasier"
date: "2023-10-17"
output: html_document
---

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```


## Model1
Find an equation that expresses SIMS as a function of arm strength.

## REsults 

## Graphical Results 

```{r}
plot(SIMS~ARM,data=data)
```
As arm strengthh increases the sims score also increases. This is a positive trend between arm strength and sims score.

## Numerical Results

```{r}
cor(data$SIMS, data$ARM,)
```

We have a positive correlation, with scattered.

## Inference 
```{r}
Model1 = lm(SIMS~ARM, data = data)
print(summary(Model1))
```


```{r}
plot(SIMS~ARM,data=data)
abline(Model1, col='purple')
```
The line and the data shows the best linear fits. If you increase arm score by 1 sims score goes up by 0.05